Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
casted -> cast

Another approach is to combine the projection matrices issued from the processing of the projection algorithm over the 31 reference clusterings. As the number of classes can vary between reference clusterings, the kind of combination is not feasible using the LDA method. On the contrary, the LMNN method always outputs a projection matrix with equal dimensions. Those projection matrices being of the same dimensionality they can safely be averaged to estimate an consensus projection.

@@

Our problem is thus casted into a ranking problem, where from several candidates, the algorithm is asked to provide a ranking list of those candidates, sorted by similarity.

>>>>

Another approach is to combine the projection matrices issued from the processing of the projection algorithm over the 31 reference clusterings. As the number of classes can vary between reference clusterings, the kind of combination is not feasible using the LDA method. On the contrary, the LMNN method always outputs a projection matrix with equal dimensions. Those projection matrices being of the same dimensionality they can safely be averaged to estimate a consensus projection.

\vl{What does "safely" mean here? We are at the epicenter of the paper here, every word matters. @writing}

@@

Our problem is thus cast into a ranking problem, where from several candidates, the algorithm is asked to provide a ranking list of those candidates, sorted by similarity.
